Exploring the Pareto front of multi-objective COVID-19 mitigation policies using reinforcement learning

### 2023-02-02 paper/main.tex
processed pieters comments (section 4.)

Similar to classification, PCN requires a labeled dataset with training examples to learn a mapping from input to label. However, contrary to classification, the data present in the dataset is not fixed. \added{PCN collects data from the trajectories experienced while exploring the environment. Thus, the dataset improves over time, as we collect better and better trajectories.}

\added{Concretely, the PCN algorithm is a loop that repeats 3 main steps:
\begin{enumerate}
    \item Using the current policy to interact with the environment and generate trajectories
    \item Update and prune the dataset to incorporate these new trajectories and remove the least interesting trajectories in terms of returns
    \item Update the policy by training it on the updated dataset
\end{enumerate}
}

>>>>

Similar to classification, PCN requires a labeled dataset with training examples to learn a mapping from input to label. However, contrary to classification, the data present in the dataset is not fixed. \added{PCN collects data from the trajectories experienced while exploring the environment. Thus, the dataset improves over time, as we collect increasingly better trajectories.}

\added{Concretely, the PCN algorithm is a loop that repeatedly executes 3 main steps:
\begin{enumerate}
    \item Use the current policy to interact with the environment and generate trajectories (see Section~\ref{sec:pcn-policy-exploration}).
    \item Update the dataset to incorporate these new trajectories and prun the least interesting trajectories in terms of returns (see Section~\ref{sec:pcn-building-dataset}).
    \item Update the policy by training it on the updated dataset (see Section~\ref{sec:pcn-continuous}).
\end{enumerate}
}
